---
title: "Data Science w00t"
author: "Roxanne Stockard-Hicks"
date: 2015-07-23T21:13:14-05:00
categories: ["intro"]

---
###Histograms

First, you need to load the necessary packages:
```{r}
library(Lahman)
library(ggplot2)
library(sqldf)
```

Now, pick the parameter you'd like to look at, which here is weight for all players:
```{r}
query<-"SELECT weight
 FROM Master"

 result<-sqldf(query)
```

Last, create a bar plot for frequency of all weights in the Lahman database:

```{r}
ggplot()+
   geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=50) +
   ggtitle("Body weight")
```

###Time Series

First again, we need to load the necessary packages:
```{r}
library(Lahman)
library(ggplot2)
library(sqldf)
```

Pick the data we want, in this case number of home runs Babe Ruth made each year he played baseball:
```{r}
 query<-"SELECT yearID,HR
 FROM Batting
 WHERE playerID='ruthba01'"

 result<-sqldf(query)
```
 
 Last, here is how to make a time series chart with this information:
```{r}
 ggplot()+
   geom_point(data=result,aes(x=yearID,y=HR))+
   geom_line(data=result,aes(x=yearID,y=HR))+
   ggtitle("Ruths Homeruns")+
   xlab("Year")+
   ylab("Homeruns")
```

###Bar Plots

It's good to start out with loading packages every time you start a project, just be sure everything is there and roped in with the library:
```{r}
library(Lahman)
library(ggplot2)
library(sqldf)
```

Here is the search for data for our bar plot.  We are looking for all the stolen bases each year by one player, loftoke01:
```{r}
query<-"SELECT teamID,sum(SB) AS total_SB
FROM Batting
WHERE playerID='loftoke01'
GROUP BY teamID
ORDER BY sum(SB)"

result<-sqldf(query)
```

Here's the preliminary coding for a bar plot:
```{r}
result$teamID<-factor(result$teamID,levels=result$teamID)
```

And now the bar plot itself:
```{r}

ggplot()+
  geom_bar(data=result,aes(x=teamID,y=total_SB),stat='identity')
```

###Scatterplots

Set-up:
```{r}
library(ggplot2)
library(Lahman)
library(sqldf)
```
######Setup
First, let's set up some randomized data points:

```{r}
x<-rnorm(100,5,2)
y<-rnorm(100,2*x+1,2)

x
```

```{r}
y
```
######Progress
Now let's make the data frame:

```{r}
df<-data.frame(x,y)

df
```

######Results!
Finally, the scatterplot!

```{r}
ggplot()+
geom_point(data=df,aes(x,y))
```


